---
title: Descriptives Report 1
date: "Date: `r Sys.Date()`"
output:
  # radix::radix_article: # radix is a newer alternative that has some advantages over `html_document`.
  html_document:
    keep_md: yes
    toc: 4
    toc_float: true
    number_sections: true
# css: ../common/styles.css         # analysis/common/styles.css
---

  This report covers the analyses used in the ZZZ project (Marcus Mark, PI).

<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of two directories.-->
```{r, echo=F, message=F}
# cat("Working directory: ", getwd())
library(knitr)
opts_knit$set(root.dir = "../../")  #Don't combine this call with any other chunk -especially one that uses file paths.
```

<!-- Set the report-wide options, and point to the external code file. -->
```{r set-options, echo=F}
# cat("Working directory: ", getwd())
report_render_start_time <- Sys.time()
opts_chunk$set(
  results      = "show",
  comment      = NA,
  tidy         = FALSE,
  # dpi        = 400,
  # out.width  = "650px", #This affects only the markdown, not the underlying png file.  The height will be scaled appropriately.
  fig.width    = 4,
  fig.height   = 4,
  fig.path     = "figure-png/"
)

echo_chunks    <- FALSE # Toggle for debugging.
message_chunks <- FALSE # Toggle for debugging.
# options(width=100) # So the output is 25% wider than the default.
read_chunk("./analysis/descriptives-1/descriptives-1.R") # This allows knitr to call chunks tagged in the underlying *.R file.
```

<!-- Load 'sourced' R files.  Suppress the output when loading sources. -->
```{r load-sources, echo=echo_chunks, message=message_chunks}
```

<!-- Load packages, or at least verify they're available on the local machine.  Suppress the output when loading packages. -->
```{r load-packages, echo=echo_chunks, message=message_chunks}
```

<!-- Load any global functions and variables declared in the R file.  Suppress the output. -->
```{r declare-globals, echo=echo_chunks, results='show', message=message_chunks}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. -->
```{r rmd-specific, echo=echo_chunks, message=message_chunks}
# Put presentation-specific code in here.  It doesn't call a chunk in the codebehind file.
#   It should be rare (and used cautiously), but sometimes it makes sense to include code in Rmd
#   that doesn't live in the codebehind R file.
```

<!-- Load the datasets.   -->
```{r load-data, echo=echo_chunks, results='show', message=message_chunks}
```

<!-- Tweak the datasets.   -->
```{r tweak-data, echo=echo_chunks, results='show', message=message_chunks}
```

Summary {.tabset .tabset-fade .tabset-pills}
===========================================================================

Notes
---------------------------------------------------------------------------

1. The current report covers `r nrow(ds_patient)` patients, with `r dplyr::n_distinct(ds_patient$data_partner_id)` unique values for `data_partner_id`.


Unanswered Questions
---------------------------------------------------------------------------

Answered Questions
---------------------------------------------------------------------------


Univariate
===========================================================================

`person` table
---------------------------------------------------------------------------

```{r marginals-person, echo=echo_chunks, message=message_chunks}
```

`patient` table
---------------------------------------------------------------------------

```{r marginals-patient, echo=echo_chunks, message=message_chunks}
```

`patient_latent` table
---------------------------------------------------------------------------

```{r marginals-patient_latent, echo=echo_chunks, message=message_chunks}
```

`site_latent` table
---------------------------------------------------------------------------

```{r marginals-site_latent, echo=echo_chunks, message=message_chunks}
```


Multivariate
===========================================================================

Scatterplots
---------------------------------------------------------------------------

```{r scatterplots, echo=echo_chunks, message=message_chunks, fig.width=7}
```


Correlation Matrixes
---------------------------------------------------------------------------

```{r correlation-matrixes, echo=echo_chunks, message=message_chunks, fig.width=9, fig.height=9, results='asis'}
```


Models
===========================================================================

Model Exploration
---------------------------------------------------------------------------
```{r models, echo=echo_chunks, message=message_chunks}
```


Final Model
---------------------------------------------------------------------------

```{r model-results-table, echo=echo_chunks, message=message_chunks, warning=TRUE}
```



Session Information {#session-info}
===========================================================================

For the sake of documentation and reproducibility, the current report was rendered in the following environment.  Click the line below to expand.

  <details>
    <summary>Environment <span class="glyphicon glyphicon-plus-sign"></span></summary>
    ```{r session-info, echo=FALSE}
    if (requireNamespace("sessioninfo", quietly = TRUE)) {
      sessioninfo::session_info(include_base = TRUE)
    } else {
      sessionInfo()
    }
    ```
  </details>

```{r session-duration, echo=FALSE}
report_render_duration_in_seconds <- as.integer(difftime(Sys.time(), report_render_start_time, units="secs"))
```

Report rendered by `r Sys.info()["user"]` at `r strftime(Sys.time(), "%Y-%m-%d, %H:%M %z")` in `r report_render_duration_in_seconds` seconds.
